
\pagebreak
\begin{thebibliography}{9}
  \bibitem{mainpaper} 
  Brendan D. McKay, Stanisław P. Radziszowski. 
  \textit{R(4,5) = 25}. 
  
  \bibitem{nauty} 
  Brendan D. McKay.
  \textit{nauty user's guide (version 2.4)}.  
  Department of Computer Science
  Australian National University
  Canberra ACT 0200, Australia
  November 4, 2009

  \bibitem{smallramsey} 
  Stanisław P. Radziszowski.
  \textit{Small Ramsey Numbers}.  
  Department of Computer Science Rochester Institute of Technology Rochester, NY 14623
  June 11, 1994

  \bibitem{cykl4} 
  Janusz Dybizbański.
  \textit{Liczby Ramseya z cyklem C4}.  
  Uniwersytet Warszawski
  Wydział Matematyki, Informatyki i Mechaniki
  Listopad 2013

  \bibitem{numbers} 
  Christos Nestor Chachamis.
  \textit{Ramsey Numbers}.  
  May 13, 2018

  \bibitem{theory} 
  Lane Barton IV
  \textit{Ramsey Theory}.  
  May 13, 2016

  \bibitem{generation} 
  Brendan D. McKay
  \textit{ISOMORPH-FREE EXHAUSTIVE GENERATION}.  
  May 13, 2016
  
     \bibitem{erdogranica} 
  P.  Erdősa,  Some  Remarks  on  the  Theory  of  Graphs,
  \textit{Bulletin  of  the  American  Mathematical  Society},
  53(4):292–294,  1947
  
    \bibitem{graniceupdown} 
  Christos Nestor Chachamis
  \textit{Ramsey Numbers}.  
  May 13, 2018

 \bibitem{ramsey} 
 Ramsey, F.P. (1930), 
 \textit{On a Problem of Formal Logic.}
 Proceedings of the London Mathematical Society, s2-30: 264-286. https://doi.org/10.1112/plms/s2-30.1.264
 
 \bibitem{erdoshappy} 
 Erdős, P.; Szekeres, G.
 A combinatorial problem in geometry. Compositio Mathematica, Volume 2 (1935) , pp. 463-470.
  
   \bibitem{aliens} 
  \textit{Ramsey Theory}
   by Ronald L. Graham and Joel H. Spencer, in Scientific American (July 1990), p. 112-117
   
   \bibitem{OEIS}
       OEIS Foundation Inc. (2020), The On-Line Encyclopedia of Integer Sequences, http://oeis.org/A000088.

  \bibitem{canon}
       Nicolas Bloyet, Pierre-François Marteau, Emmanuel Frenod. Scott : A method for representing graphs
      as rooted trees for graph canonization. COMPLEX NETWORKS 2019, Springer, pp.578-590, 2019,
      Studies in Computational Intelligence Series, $ff10.1007/978-3-030-36687-2_48ff. ffhal-02314658f$
      
   \bibitem{partyproblem}
       Rich Wolski "CS290I Lecture notes -- Ramsey Numbers: Top Hits Played at Parties Thrown by Paul Erdos" https://sites.cs.ucsb.edu/~rich/class/cs293-cloud/notes/Ramsey/index.html

\bibitem{partyformal}
 Weisstein, Eric W. "Party Problem." From MathWorld--A Wolfram Web Resource. https://mathworld.wolfram.com/PartyProblem.html 
 
 \bibitem{boundproof}
 Brendan D McKay, Stanisław P Radziszowski,
Subgraph Counting Identities and Ramsey Numbers,
Journal of Combinatorial Theory, Series B,
Volume 69, Issue 2,
1997,
Pages 193-209,
ISSN 0095-8956,
https://doi.org/10.1006/jctb.1996.1741.
(http://www.sciencedirect.com/science/article/pii/S0095895696917414)

 \bibitem{computeproof}
Charles M Grinstead, Sam M Roberts,
On the Ramsey numbers R(3, 8) and R(3, 9),
Journal of Combinatorial Theory, Series B,
Volume 33, Issue 1,
1982,
Pages 27-51,
ISSN 0095-8956,
https://doi.org/10.1016/0095-8956(82)90055-7.
(http://www.sciencedirect.com/science/article/pii/0095895682900557)






  \end{thebibliography}